---
title: CV
date: last-modified
author: Lorenzo Fabbri
email: lorenzo.fabbri@isglobal.org
orcid: 0000-0003-3031-322X
scholar: QbPv1H0AAAAJ
github: lorenzoFabbri
jobtitle: PhD Student

fontawesome: yes

format:
  pdf:
    pdf-engine: xelatex
    documentclass: article
    fontsize: 11pt
    include-in-header:
      - partials/include-in-header.tex
    template-partials:
      - partials/before-body.tex
    filters:
      - partials/styles.lua
    citeproc: false
    cite-method: biblatex

bibliography: bibliography.bib
csl: partials/ama11.csl

execute:
  echo: false

editor_options:
  chunk_output_type: console

validate-yaml: false
---

```{r}
cvevents <- function(tbl, what, when, where, details) {
  command_start <- "\\cvevent"
  res <- paste0(
    command_start,
    "{", tbl[[when]], "}",
    "{", tbl[[what]], "}",
    "{", tbl[[where]], "}"
  )
  
  tbl[[details]] <- sapply(
    tbl[[details]], function(x) {
      paste0("{", x, "}", collapse = ",")
    }
  )
  res <- paste0(res, "{", tbl[[details]], "}")
  
  cat(res, sep = "\n")
}

cvshortevents <- function(tbl, what, when, where) {
  command_start <- "\\cvshortevent"
  res <- paste0(
    command_start,
    "{", tbl[[when]], "}",
    "{", tbl[[what]], "}",
    "{", tbl[[where]], "}"
  )
  
  cat(res, sep = "\n")
}
```

```{r}
my_orcid <- "0000-0003-3031-322X"
my_googlescholar <- "QbPv1H0AAAAJ"
```

# Academic Appointments

\vspace{-0.5em}
\rule{\linewidth}{0.5pt}

```{r}
#| label: work_experience
#| output: asis

exp_raw <- rorcid::orcid_employments(orcid = my_orcid)
exp_ <- exp_raw[[my_orcid]]$`affiliation-group`$summaries |>
  dplyr::bind_rows() |>
  tibble::as_tibble() |>
  janitor::clean_names() |>
  dplyr::mutate(
    employment_summary_end_date_year_value = tidyr::replace_na(
      employment_summary_end_date_year_value, "Present"
    ),
    location = paste0(
      employment_summary_organization_name,
      " (",
      employment_summary_organization_address_city,
      ", ",
      employment_summary_organization_address_country,
      ")"
    ),
    dates = paste0(
      employment_summary_start_date_year_value,
      " - ",
      employment_summary_end_date_year_value
    )
  ) |>
  cvshortevents(
    what = "employment_summary_role_title",
    when = "dates",
    where = "location"
  )
```

<!-- # Research Visits -->

<!-- ```{r} -->
<!-- #| label: research_visits -->
<!-- #| output: asis -->

<!-- visits_raw <- rorcid::orcid_invited_positions(orcid = my_orcid) -->
<!-- visits <- visits_raw[[my_orcid]]$`affiliation-group`$summaries |> -->
<!--   dplyr::bind_rows() |> -->
<!--   tibble::as_tibble() |> -->
<!--   janitor::clean_names() |> -->
<!--   dplyr::mutate( -->
<!--     invited_position_end_date_year_value = tidyr::replace_na( -->
<!--       invited_position_summary_end_date_year_value, "Present" -->
<!--     ), -->
<!--     location = paste0( -->
<!--       invited_position_summary_organization_name, -->
<!--       " (", -->
<!--       invited_position_summary_organization_address_city, -->
<!--       ", ", -->
<!--       invited_position_summary_organization_address_country, -->
<!--       ")" -->
<!--     ), -->
<!--     dates = paste0( -->
<!--       invited_position_summary_start_date_year_value, -->
<!--       " - ", -->
<!--       invited_position_summary_end_date_year_value -->
<!--     ) -->
<!--   ) |> -->
<!--   cvshortevents( -->
<!--     what = "invited_position_summary_role_title", -->
<!--     when = "dates", -->
<!--     where = "location" -->
<!--   ) -->
<!-- ``` -->

# Grants and Fellowships

\vspace{-0.5em}
\rule{\linewidth}{0.5pt}

```{r}
#| label: funding
#| output: asis

funds_raw <- rorcid::orcid_fundings(orcid = my_orcid)
funds <- funds_raw[[my_orcid]]$group$`funding-summary` |>
  dplyr::bind_rows() |>
  tibble::as_tibble() |>
  janitor::clean_names() |>
  dplyr::mutate(
    location = paste0(
      organization_name,
      " (",
      organization_address_city,
      ", ",
      organization_address_country,
      ")"
    )
  ) |>
  dplyr::arrange(
    dplyr::desc(start_date_year_value),
    title_title_value
  ) |>
  cvshortevents(
    what = "title_title_value",
    when = "start_date_year_value",
    where = "location"
  )
```

# Honors and Awards

\vspace{-0.5em}
\rule{\linewidth}{0.5pt}

```{r}
#| label: honors
#| output: asis

honors_raw <- rorcid::orcid_distinctions(orcid = my_orcid)
honors <- honors_raw[[my_orcid]]$`affiliation-group`$summaries |>
  dplyr::bind_rows() |>
  tibble::as_tibble() |>
  janitor::clean_names() |>
  cvshortevents(
    what = "distinction_summary_role_title",
    when = "distinction_summary_start_date_year_value",
    where = "distinction_summary_organization_name"
  )
```

# Publications

\vspace{-0.5em}
\rule{\linewidth}{0.5pt}

## Journal articles

---
nocite: |
  @*
---

\boldname{Fabbri}{Lorenzo}{L.}

::: {#refs}
:::

## Articles under review and revising

1. *Prenatal and childhood exposure to mixtures of non-persistent endocrine disrupting chemicals (EDC) and adolescence neurodevelopment: a triangulation study.*

## Software packages

```{r}
#| label: software
#| output: asis

software_raw <- rorcid::orcid_works(orcid = my_orcid)
software <- software_raw[[my_orcid]]$work |>
  dplyr::filter(type == "software") |>
  dplyr::bind_rows() |>
  tibble::as_tibble() |>
  janitor::clean_names() |>
  dplyr::select(dplyr::all_of(c(
    "title_title_value",
    "publication_date_year_value",
    "url_value"
  ))) |>
  dplyr::arrange(
    dplyr::desc("publication_date_year_value"),
    "title_title_value"
  ) |>
  cvshortevents(
    what = "title_title_value",
    when = "publication_date_year_value",
    where = "url_value"
  )
```

# Conferences, Workshops, and Talks

\vspace{-0.5em}
\rule{\linewidth}{0.5pt}

## Research presentations and conference participation

See [https://figshare.com/authors/Lorenzo_Fabbri](https://figshare.com/authors/Lorenzo_Fabbri/11879642) for posters.

```{r}
#| label: posters
#| output: asis

conf <- tibble::tribble(
  ~what, ~when, ~where,
  "A precision environmental health approach to childhood obesity and metabolic dysfunction: identifying biological pathways and prenatal determinants", "2024", "ISEE Annual Conference, Santiago (CL)",
  "Prenatal Exposure to Chemical Mixtures and Metabolic Syndrome Risk in European Children", "2024", "ISEE Annual Conference, Santiago (CL)",
  "Childhood exposure to non-persistent endocrine disrupting chemicals and multi-omic profiles: a panel study", "2022", "ISEE Annual Conference, Athens (GR)",
  "Childhood exposure to non-persistent endocrine disrupting chemicals and multi-omic markers in a population-based child cohort", "2022", "EURION Cluster Annual Meeting (online)",
  "Childhood exposure to non-persistent endocrine disrupting chemicals and multi-omic markers in a population-based child cohort", "2022", "International Prenatal Programing and Toxicity Meeting (online)",
  "Efficient and Portable MPI Support for Approximate Bayesian Computation", "2017", "Platform for Advanced Scientific Computing Conference, Lugano (CH)"
) |>
  dplyr::arrange(dplyr::desc(when)) |>
  cvshortevents(
    what = "what",
    when = "when",
    where = "where"
  )
```

## Talks and workshops

See [https://github.com/lorenzoFabbri/talks](https://github.com/lorenzoFabbri/talks) for slides and materials.

```{r}
#| label: talks
#| output: asis

talks <- tibble::tribble(
  ~what, ~when, ~where,
  "Transparent causal inference for observational epidemiology", "01/2025", "Colicino Group, NYC (via Zoom)"
) |>
  dplyr::mutate(
    when = lubridate::my(when)
  ) |>
  dplyr::arrange(dplyr::desc(when)) |>
  dplyr::mutate(
    when = format(as.Date(when), "%b %Y")
  ) |>
  cvshortevents(
    what = "what",
    when = "when",
    where = "where"
  )
```

# Education

\vspace{-0.5em}
\rule{\linewidth}{0.5pt}

```{r}
#| label: education
#| output: asis

edu_raw <- rorcid::orcid_educations(orcid = my_orcid)
edu <- edu_raw[[my_orcid]]$`affiliation-group`$summaries |>
  dplyr::bind_rows() |>
  tibble::as_tibble() |>
  janitor::clean_names() |>
  dplyr::mutate(
    education_summary_end_date_year_value = tidyr::replace_na(
      education_summary_end_date_year_value, "Present"
    ),
    education_summary_organization_name = stringr::str_replace_all(
      education_summary_organization_name, "\\&", "and"
    ),
    location = paste0(
      education_summary_organization_name,
      " (",
      education_summary_organization_address_city,
      ", ",
      education_summary_organization_address_country,
      ")"
    ),
    dates = paste0(
      education_summary_start_date_year_value,
      " - ",
      education_summary_end_date_year_value
    ),
    details = list(
      c(
        "Epidemiology by Distance Learning - Individual modules.",
        "Fundamentals of Epidemiology (EPM101). Practical Epidemiology (EPM103)."
      ), # LSHTM
      c(
        "Mathematical statistics (M347)."
      ), # OU UK
      c(
        "Supervisor: Prof. Martine Vrijheid."
      ),
      c(
        "Thesis (FBK, Trento (IT)): Machine Learning for Predictive Drug Induced Hepatotoxicity. Supervised by: Dr. Cesare Furlanello, Dr. Marco Chierici, Prof. Enrico Domenici.",
        "Internship (HITS, Heidelberg (DE)): Machine and Deep Learning for Predictive Unbinding Kinetics of Kinases. Supervised by: Prof. Rebecca Wade, Dr. Daria Kokh, Prof. Raffaello Potestio.",
        "Final mark: 110/110 With Honors."
      ),
      c(
        "Project (USI, Lugano (CH)): Investigation by Computational Techniques of Channelopaties related to Sodium Channels. Supervised by: Prof. Vittorio Limongelli, Prof. Daniele Di Marino."
      ),
      c(
        "Thesis (RWTH, Aachen (DE)):  Whole Body PBPK Modeling of Valproic Acid. Supervised by: Prof. Elena Maestri, Prof. Lars M. Blank, Dr. Henrik Cordes.",
        "Final mark: 103/110."
      )
    )
  ) |>
  cvevents(
    what = "education_summary_role_title",
    when = "dates",
    where = "location",
    details = "details"
  )
```

# Continuing Education

\vspace{-0.5em}
\rule{\linewidth}{0.5pt}

```{r}
#| label: cont_edu
#| output: asis

cont_edu <- tibble::tribble(
  ~what, ~when, ~where,
  "Spring School in Causal Inference with Observational Data", "04/2022", "Causal Insights, Leeds (UK)",
  "Computational Bayesian methods using brms in R", "02/2022", "Physalia Courses, online",
  "ELIXIR Omics Integration and Systems Biology", "09/2021", "National Bioinformatics Infrastructure Sweden, online",
  "Advanced Statistics: Statistical Modelling", "08/2021", "Swiss Institute of Bioinformatics, online",
  "Alpine Exposome Summer School", "06/2021", "Inserm and ATHLETE, online",
  "Metabolomics Data Processing and Data Analysis", "02/2021", "University of Birmingham, online",
  "Mendelian Randomisation", "05/2020", "Imperial College London, online",
  "Image Analysis and Modeling of Complex Biological Dynamics", "09/2017", "University of Wurzburg, Wurzburg (DE)",
  "Effective High Performance Computing Summer School", "07/2017", "CSCS and University of Lugano, Lugano (CH)",
  "MARVEL School on Variationally Enhanced Sampling", "02/2017", "University of Lugano, Lugano (CH)",
  "Advanced Course in Alternatives to Animal Experimentation", "11/2015", "University of Genova, Genoa (IT)"
) |>
  dplyr::mutate(
    when = lubridate::my(when)
  ) |>
  dplyr::arrange(dplyr::desc(when)) |>
  dplyr::mutate(
    when = format(as.Date(when), "%b %Y")
  ) |>
  cvshortevents(
    what = "what",
    when = "when",
    where = "where"
  )
```

# Service

\vspace{-0.5em}
\rule{\linewidth}{0.5pt}

## Referee

*Scientific Reports* (1).

## Working groups

```{r}
#| label: service
#| output: asis

service_raw <- rorcid::orcid_services(orcid = my_orcid)
service <- service_raw[[my_orcid]]$`affiliation-group` |>
  dplyr::bind_rows() |>
  tibble::as_tibble() |>
  tidyr::unnest(cols = "summaries") |>
  janitor::clean_names() |>
  dplyr::arrange(
    dplyr::desc(service_summary_start_date_year_value),
    dplyr::desc(service_summary_end_date_year_value)
  ) |>
  dplyr::mutate(
    summary_end_date_year_value = tidyr::replace_na(
      service_summary_end_date_year_value, "Present"
    ),
    dates = paste0(
      service_summary_start_date_year_value,
      " - ",
      summary_end_date_year_value
    ),
    summary_role_title = service_summary_role_title,
    summary_organization_name = service_summary_organization_name
  ) |>
  cvshortevents(
    what = "summary_organization_name",
    when = "dates",
    where = "summary_role_title"
  )
```

## Professional memberships

```{r}
#| label: memberships
#| output: asis

memberships_raw <- rorcid::orcid_memberships(orcid = my_orcid)
memberships <- memberships_raw[[my_orcid]]$`affiliation-group` |>
  dplyr::bind_rows() |>
  tibble::as_tibble() |>
  tidyr::unnest(cols = "summaries") |>
  janitor::clean_names() |>
  dplyr::arrange(
    dplyr::desc(membership_summary_start_date_year_value),
    dplyr::desc(membership_summary_end_date_year_value)
  ) |>
  dplyr::mutate(
    summary_end_date_year_value = tidyr::replace_na(
      membership_summary_end_date_year_value, "Present"
    ),
    dates = paste0(
      membership_summary_start_date_year_value,
      " - ",
      summary_end_date_year_value
    ),
    summary_role_title = "Member",
    summary_organization_name = membership_summary_organization_name
  ) |>
  cvshortevents(
    what = "summary_organization_name",
    when = "dates",
    where = "summary_role_title"
  )
```

# Skills

\vspace{-0.5em}
\rule{\linewidth}{0.5pt}

```{r}
skills <- tibble::tribble(
  ~what, ~details,
  "Languages", "Italian (native), English (C1, IELTS 7.0), Spanish (basic)",
  "Programming Languages", "R, Python, MATLAB, C",
  "Markup Languages", "LaTeX, Quarto/RMarkdown",
  "Software Development", "git, SLURM, High Performance Scientific Computing"
) |>
  as.data.frame()
colnames(skills) <- NULL

tinytable::tt(skills) |>
  tinytable::theme_tt(
    theme = "void"
  ) |>
  tinytable::style_tt(
    j = 1,
    bold = TRUE
  )
```
