---
title: CV
date: last-modified
author: Lorenzo Fabbri
email: lorenzo.fabbri@isglobal.org
orcid: 0000-0003-3031-322X
scholar: QbPv1H0AAAAJ
github: lorenzoFabbri
jobtitle: Postdoctoral Fellow

fontawesome: yes

format:
  pdf:
    pdf-engine: xelatex
    documentclass: article
    fontsize: 11pt
    include-in-header:
      - partials/include-in-header.tex
    template-partials:
      - partials/before-body.tex
    filters:
      - partials/styles.lua
    citeproc: false
    cite-method: biblatex
    biblatexoptions:
      - backend = biber
      - maxnames = 99
      - sorting = ydnt
      - sortlocale = en-GB

bibliography: bibliography.bib

execute:
  echo: false
  warning: false
  error: false

editor_options:
  chunk_output_type: console

validate-yaml: false
---

```{r}
#| results: asis

source("helpers.R")

my_orcid <- "0000-0003-3031-322X"
my_googlescholar <- "QbPv1H0AAAAJ"
```

# Research Interests

\vspace{-0.5em}
\rule{\linewidth}{0.5pt}

* Environmental and social determinants of **cancer**.
* Transparent **causal** inference and evidence **triangulation**.

# Academic Appointments

\vspace{-0.5em}
\rule{\linewidth}{0.5pt}

```{r}
#| results: asis
#| label: work_experience

render_orcid_section(
  fetch_fun = rorcid::orcid_employments,
  orcid = my_orcid,
  summaries_path = c(my_orcid, "affiliation-group", "summaries"),
  mapping = list(
    what = "employment_summary_role_title",
    org = "employment_summary_organization_name",
    city = "employment_summary_organization_address_city",
    country = "employment_summary_organization_address_country",
    start_month = "employment_summary_start_date_month_value",
    start_year = "employment_summary_start_date_year_value",
    end_month = "employment_summary_end_date_month_value",
    end_year = "employment_summary_end_date_year_value"
  ),
  arrange_desc_cols = c("employment_summary_start_date_year_value"),
  short = TRUE,
  show_present = TRUE
)
```

# Education

\vspace{-0.5em}
\rule{\linewidth}{0.5pt}

```{r}
#| results: asis
#| label: education

# Hard-coded details for each education entry
education_details <- list(
  c(),
  c(),
  c("Basic Epidemiology (PHM101)."),
  c("Mathematical statistics (M347): 91/100 With Distinction."),
  c("Thesis: Early Life Exposure to Environmental Chemicals and Neurodevelopment through Childhood and Adolescence.", "Supervisor: Prof. Martine Vrijheid."),
  c("Thesis (FBK, Trento (IT)): Machine Learning for Predictive Drug Induced Hepatotoxicity. Supervised by: Dr. Cesare Furlanello, Dr. Marco Chierici, Prof. Enrico Domenici.", "Internship (HITS, Heidelberg (DE)): Machine and Deep Learning for Predictive Unbinding Kinetics of Kinases. Supervised by: Prof. Rebecca Wade, Dr. Daria Kokh, Prof. Raffaello Potestio.", "Final mark: 110/110 With Honors."),
  c("Project (USI, Lugano (CH)): Investigation by Computational Techniques of Channelopaties related to Sodium Channels. Supervised by: Prof. Vittorio Limongelli, Prof. Daniele Di Marino."),
  c("Thesis (RWTH, Aachen (DE)):  Whole Body PBPK Modeling of Valproic Acid. Supervised by: Prof. Elena Maestri, Prof. Lars M. Blank, Dr. Henrik Cordes.", "Final mark: 103/110.")
)

render_orcid_section(
  fetch_fun = rorcid::orcid_educations,
  orcid = my_orcid,
  summaries_path = c(my_orcid, "affiliation-group", "summaries"),
  mapping = list(
    what = "education_summary_role_title",
    org = "education_summary_organization_name",
    city = "education_summary_organization_address_city",
    country = "education_summary_organization_address_country",
    start_month = "education_summary_start_date_month_value",
    start_year = "education_summary_start_date_year_value",
    end_month = "education_summary_end_date_month_value",
    end_year = "education_summary_end_date_year_value"
  ),
  arrange_desc_cols = c("education_summary_start_date_year_value"),
  short = FALSE,
  details_override = education_details,
  show_present = TRUE
)
```

# Research Visits

\vspace{-0.5em}
\rule{\linewidth}{0.5pt}

```{r}
#| results: asis
#| label: research_visits

render_orcid_section(
  fetch_fun = rorcid::orcid_invited_positions,
  orcid = my_orcid,
  summaries_path = c(my_orcid, "affiliation-group", "summaries"),
  mapping = list(
    what = "invited_position_summary_role_title",
    org = "invited_position_summary_organization_name",
    city = "invited_position_summary_organization_address_city",
    country = "invited_position_summary_organization_address_country",
    start_month = "invited_position_summary_start_date_month_value",
    start_year = "invited_position_summary_start_date_year_value",
    end_month = "invited_position_summary_end_date_month_value",
    end_year = "invited_position_summary_end_date_year_value"
  ),
  arrange_desc_cols = c("invited_position_summary_start_date_year_value"),
  short = TRUE,
  show_present = TRUE
)
```

# Grants and Fellowships

\vspace{-0.5em}
\rule{\linewidth}{0.5pt}

```{r}
#| results: asis
#| label: funding

render_orcid_section(
  fetch_fun = rorcid::orcid_fundings,
  orcid = my_orcid,
  summaries_path = c(my_orcid, "group", "funding-summary"),
  mapping = list(
    what = "title_title_value",
    org = "organization_name",
    city = "organization_address_city",
    country = "organization_address_country",
    start_month = "start_date_month_value",
    start_year = "start_date_year_value",
    end_month = "end_date_month_value",
    end_year = "end_date_year_value"
  ),
  arrange_desc_cols = c("start_date_year_value"),
  short = TRUE,
  show_present = TRUE
)
```

# Honors and Awards

\vspace{-0.5em}
\rule{\linewidth}{0.5pt}

```{r}
#| results: asis
#| label: honors

render_orcid_section(
  fetch_fun = rorcid::orcid_distinctions,
  orcid = my_orcid,
  summaries_path = c(my_orcid, "affiliation-group", "summaries"),
  mapping = list(
    what = "distinction_summary_role_title",
    org = "distinction_summary_organization_name",
    city = NULL,
    country = NULL,
    start_month = "distinction_summary_start_date_month_value",
    start_year = "distinction_summary_start_date_year_value",
    end_month = "distinction_summary_end_date_month_value",
    end_year = "distinction_summary_end_date_year_value"
  ),
  arrange_desc_cols = c("distinction_summary_start_date_year_value"),
  short = TRUE
)
```

# Publications

\vspace{-0.5em}
\rule{\linewidth}{0.5pt}

## Journal articles

---
nocite: |
  @*
---

\boldname{Fabbri}{Lorenzo}{L.}

::: {#refs}
:::

## Articles under review and revising

1. Distinct tumor microenvironment signatures predict outcomes and correlate with PD-L1 in HPV-independent vulvar cancer.

## Software packages

```{r}
#| results: asis
#| label: software

software_raw <- rorcid::orcid_works(orcid = my_orcid)
software <- software_raw[[my_orcid]]$work |>
  dplyr::filter(type == "software") |>
  dplyr::bind_rows() |>
  tibble::as_tibble() |>
  janitor::clean_names() |>
  dplyr::select(dplyr::all_of(c(
    "title_title_value",
    "publication_date_year_value",
    "url_value"
  ))) |>
  dplyr::arrange(
    dplyr::desc(.data$publication_date_year_value),
    .data$title_title_value
  ) |>
  cvshortevents(
    what = "title_title_value",
    when = "publication_date_year_value",
    where = "url_value"
  )
```

# Conferences, Workshops, and Talks

\vspace{-0.5em}
\rule{\linewidth}{0.5pt}

## Research presentations and conference participation

```{r}
#| results: asis
#| label: posters

conf <- tibble::tribble(
  ~what, ~when, ~where,
  "A precision environmental health approach to childhood obesity and metabolic dysfunction: identifying biological pathways and prenatal determinants", "2024", "ISEE Annual Conference, Santiago (CL)",
  "Prenatal Exposure to Chemical Mixtures and Metabolic Syndrome Risk in European Children", "2024", "ISEE Annual Conference, Santiago (CL)",
  "Childhood exposure to non-persistent endocrine disrupting chemicals and multi-omic profiles: a panel study", "2022", "ISEE Annual Conference, Athens (GR)",
  "Childhood exposure to non-persistent endocrine disrupting chemicals and multi-omic markers in a population-based child cohort", "2022", "EURION Cluster Annual Meeting (online)",
  "Childhood exposure to non-persistent endocrine disrupting chemicals and multi-omic markers in a population-based child cohort", "2022", "International Prenatal Programing and Toxicity Meeting (online)",
  "Efficient and Portable MPI Support for Approximate Bayesian Computation", "2017", "Platform for Advanced Scientific Computing Conference, Lugano (CH)"
) |>
  dplyr::arrange(dplyr::desc(when)) |>
  cvshortevents(
    what = "what",
    when = "when",
    where = "where"
  )
```

## Talks and workshops

See [https://github.com/lorenzoFabbri/talks](https://github.com/lorenzoFabbri/talks) for slides and materials.

```{r}
#| results: asis
#| label: talks

talks <- tibble::tribble(
  ~what, ~when, ~where,
  "Transparent causal inference for observational epidemiology", "01/2025", "Colicino Group, NYC (via Zoom)"
) |>
  dplyr::mutate(when = lubridate::my(when)) |>
  dplyr::arrange(dplyr::desc(when)) |>
  dplyr::mutate(when = format(as.Date(when), "%b %Y")) |>
  cvshortevents(
    what = "what",
    when = "when",
    where = "where"
  )
```

# Continuing Education

\vspace{-0.5em}
\rule{\linewidth}{0.5pt}

```{r}
#| results: asis
#| label: cont_edu

cont_edu <- tibble::tribble(
  ~what, ~when, ~where,
  "Spring School in Causal Inference with Observational Data", "04/2022", "Causal Insights, Leeds (UK)",
  "Computational Bayesian methods using brms in R", "02/2022", "Physalia Courses, online",
  "ELIXIR Omics Integration and Systems Biology", "09/2021", "National Bioinformatics Infrastructure Sweden, online",
  "Advanced Statistics: Statistical Modelling", "08/2021", "Swiss Institute of Bioinformatics, online",
  "Alpine Exposome Summer School", "06/2021", "Inserm and ATHLETE, online",
  "Metabolomics Data Processing and Data Analysis", "02/2021", "University of Birmingham, online",
  "Mendelian Randomisation", "05/2020", "Imperial College London, online",
  "Image Analysis and Modeling of Complex Biological Dynamics", "09/2017", "University of Wurzburg, Wurzburg (DE)",
  "Effective High Performance Computing Summer School", "07/2017", "CSCS and University of Lugano, Lugano (CH)",
  "MARVEL School on Variationally Enhanced Sampling", "02/2017", "University of Lugano, Lugano (CH)",
  "Advanced Course in Alternatives to Animal Experimentation", "11/2015", "University of Genova, Genoa (IT)"
) |>
  dplyr::mutate(when = lubridate::my(when)) |>
  dplyr::arrange(dplyr::desc(when)) |>
  dplyr::mutate(when = format(as.Date(when), "%b %Y")) |>
  cvshortevents(
    what = "what",
    when = "when",
    where = "where"
  )
```

# Service

\vspace{-0.5em}
\rule{\linewidth}{0.5pt}

## Referee

*Scientific Reports* (1).

## Working groups

```{r}
#| results: asis
#| label: service

render_orcid_section(
  fetch_fun = rorcid::orcid_services,
  orcid = my_orcid,
  summaries_path = c(my_orcid, "affiliation-group", "summaries"),
  mapping = list(
    what = "service_summary_role_title",
    org = "service_summary_organization_name",
    city = "service_summary_organization_address_city",
    country = "service_summary_organization_address_country",
    start_month = "service_summary_start_date_month_value",
    start_year = "service_summary_start_date_year_value",
    end_month = "service_summary_end_date_month_value",
    end_year = "service_summary_end_date_year_value"
  ),
  arrange_desc_cols = c("service_summary_start_date_year_value"),
  short = TRUE,
  show_present = TRUE
)
```

## Professional memberships

```{r}
#| results: asis
#| label: memberships

render_orcid_section(
  fetch_fun = rorcid::orcid_memberships,
  orcid = my_orcid,
  summaries_path = c(my_orcid, "affiliation-group", "summaries"),
  mapping = list(
    what = "membership_summary_organization_name",
    org = "membership_summary_organization_name",
    city = "membership_summary_organization_address_city",
    country = "membership_summary_organization_address_country",
    start_month = "membership_summary_start_date_month_value",
    start_year = "membership_summary_start_date_year_value",
    end_month = "membership_summary_end_date_month_value",
    end_year = "membership_summary_end_date_year_value"
  ),
  arrange_desc_cols = c("membership_summary_start_date_year_value"),
  short = TRUE,
  show_present = TRUE
)
```

# Skills

\vspace{-0.5em}
\rule{\linewidth}{0.5pt}

```{r}
#| label: skills

skills <- tibble::tribble(
  ~what, ~details,
  "Languages", "Italian (native), English (C1, IELTS 7.0), Spanish (basic)",
  "Programming Languages", "R, Python, MATLAB, C",
  "Markup Languages", "LaTeX, Quarto/RMarkdown",
  "Software Development", "git, SLURM, High Performance Scientific Computing"
) |>
  as.data.frame()
colnames(skills) <- NULL

tinytable::tt(skills) |>
  tinytable::theme_empty() |>
  tinytable::style_tt(j = 1, bold = TRUE)
```
