---
title: Lorenzo Fabbri
format:
  pdf:
    documentclass: article
    fontsize: 10pt
    include-in-header:
      - partials/header.tex
    filters:
      - partials/styles.lua
      - partials/dociteproc.lua
      - partials/boldname.lua
    citeproc: false
bibliography: bibliography.bib
csl: partials/ama11.csl
execute:
  echo: false
editor_options:
  chunk_output_type: console
---

```{r}
cvevents <- function(tbl, what, when, where, details) {
  command_start <- "\\cvevent"
  res <- paste0(
    command_start,
    "{", tbl[[when]], "}",
    "{", tbl[[what]], "}",
    "{", tbl[[where]], "}"
  )
  
  tbl[[details]] <- sapply(
    tbl[[details]], function(x) {
      paste0("{", x, "}", collapse = ",")
    }
  )
  res <- paste0(res, "{", tbl[[details]], "}")
  
  cat(res, sep = "\n")
}

cvshortevents <- function(tbl, what, when, where) {
  command_start <- "\\cvshortevent"
  res <- paste0(
    command_start,
    "{", tbl[[when]], "}",
    "{", tbl[[what]], "}",
    "{", tbl[[where]], "}"
  )
  
  cat(res, sep = "\n")
}
```

```{r}
my_orcid <- "0000-0003-3031-322X"
my_googlescholar <- "QbPv1H0AAAAJ"
```

# Summary

I am a PhD student at the Barcelona Institute for Global Health ([ISGlobal](https://www.isglobal.org/en#)).
I work under the supervision of Prof. [Martine Vrijheid](https://www.isglobal.org/en/our-team/-/profiles/18514).
My main topic of interest is the use of modern Causal Inference methods to answer questions in the broad field of Environmental Neuroepidemiology.
I am also profoundly interested in Open Science and Reproducible Research.

I received my Bachelor’s degree in Biotechnology and my Master’s degree in Quantitative and Computational Biology.

My personal webpage can be found [here](https://epilorenzofabbri.com). You can also find me on [Bluesky](https://bsky.app/profile/lorenzofepi.bsky.social) and [GitHub](https://github.com/lorenzoFabbri).

# Working Experience

```{r}
#| label: work_experience
#| output: asis

exp_raw <- rorcid::orcid_employments(orcid = my_orcid)
exp_ <- exp_raw$`0000-0003-3031-322X`$`affiliation-group`$summaries |>
  dplyr::bind_rows() |>
  tibble::as_tibble() |>
  janitor::clean_names() |>
  dplyr::mutate(
    employment_summary_end_date_year_value = tidyr::replace_na(
      employment_summary_end_date_year_value, "Present"
    ),
    location = paste0(
      employment_summary_organization_name,
      " (",
      employment_summary_organization_address_city,
      ", ",
      employment_summary_organization_address_country,
      ")"
    ),
    dates = paste0(
      employment_summary_start_date_year_value,
      " - ",
      employment_summary_end_date_year_value
    )
  ) |>
  cvshortevents(
    what = "employment_summary_role_title",
    when = "dates",
    where = "location"
  )
```

# Funding

```{r}
#| label: funding
#| output: asis

funds_raw <- rorcid::orcid_fundings(orcid = my_orcid)
funds <- funds_raw$`0000-0003-3031-322X`$group$`funding-summary` |>
  dplyr::bind_rows() |>
  tibble::as_tibble() |>
  janitor::clean_names() |>
  dplyr::mutate(
    location = paste0(
      organization_name,
      " (",
      organization_address_city,
      ", ",
      organization_address_country,
      ")"
    )
  ) |>
  dplyr::arrange(
    dplyr::desc(start_date_year_value),
    title_title_value
  ) |>
  cvshortevents(
    what = "title_title_value",
    when = "start_date_year_value",
    where = "location"
  )
```

# Honors and Awards

```{r}
#| label: honors
#| output: asis

honors_raw <- rorcid::orcid_distinctions(orcid = my_orcid)
honors <- honors_raw$`0000-0003-3031-322X`$`affiliation-group`$summaries |>
  dplyr::bind_rows() |>
  tibble::as_tibble() |>
  janitor::clean_names() |>
  cvshortevents(
    what = "distinction_summary_role_title",
    when = "distinction_summary_start_date_year_value",
    where = "distinction_summary_organization_name"
  )
```

# Publications

My ORCiD is [0000-0003-3031-322X](https://orcid.org/0000-0003-3031-322X).

---
nocite: |
  @*
---

::: {#refs}
:::

# Conference Presentations

The posters can be found [here](https://figshare.com/authors/Lorenzo_Fabbri/11879642).

```{r}
#| label: posters
#| output: asis

conf <- tibble::tribble(
  ~what, ~when, ~where,
  "Childhood exposure to non-persistent endocrine disrupting chemicals and multi-omic profiles: a panel study", "2022", "ISEE Annual Conference, Athens (GR)",
  "Childhood exposure to non-persistent endocrine disrupting chemicals and multi-omic markers in a population-based child cohort", "2022", "EURION Cluster Annual Meeting (online)",
  "Childhood exposure to non-persistent endocrine disrupting chemicals and multi-omic markers in a population-based child cohort", "2022", "International Prenatal Programing and Toxicity Meeting (online)",
  "Efficient and Portable MPI Support for Approximate Bayesian Computation", "2017", "Platform for Advanced Scientific Computing Conference, Lugano (CH)"
) |>
  dplyr::arrange(dplyr::desc(when)) |>
  cvshortevents(
    what = "what",
    when = "when",
    where = "where"
  )
```

# Education

```{r}
#| label: education
#| output: asis

edu_raw <- rorcid::orcid_educations(orcid = my_orcid)
edu <- edu_raw$`0000-0003-3031-322X`$`affiliation-group`$summaries |>
  dplyr::bind_rows() |>
  tibble::as_tibble() |>
  janitor::clean_names() |>
  dplyr::mutate(
    education_summary_end_date_year_value = tidyr::replace_na(
      education_summary_end_date_year_value, "Present"
    ),
    location = paste0(
      education_summary_organization_name,
      " (",
      education_summary_organization_address_city,
      ", ",
      education_summary_organization_address_country,
      ")"
    ),
    dates = paste0(
      education_summary_start_date_year_value,
      " - ",
      education_summary_end_date_year_value
    ),
    details = list(
      c(
        "Supervisor: Prof. Martine Vrijheid."
      ),
      c(
        "Thesis (FBK, Trento (IT)): Machine Learning for Predictive Drug Induced Hepatotoxicity. Supervised by: Dr. Cesare Furlanello, Dr. Marco Chierici, Prof. Enrico Domenici.",
        "Internship (HITS, Heidelberg (DE)): Machine and Deep Learning for Predictive Unbinding Kinetics of Kinases. Supervised by: Prof. Rebecca Wade, Dr. Daria Kokh, Prof. Raffaello Potestio.",
        "Final mark: 110/110 With Honors."
      ),
      c(
        "Project (USI, Lugano (CH)): Investigation by Computational Techniques of Channelopaties related to Sodium Channels. Supervised by: Prof. Vittorio Limongelli, Prof. Daniele Di Marino."
      ),
      c(
        "Thesis (RWTH, Aachen (DE)):  Whole Body PBPK Modeling of Valproic Acid. Supervised by: Prof. Elena Maestri, Prof. Lars M. Blank, Dr. Henrik Cordes.",
        "Final mark: 103/110."
      )
    )
  ) |>
  cvevents(
    what = "education_summary_role_title",
    when = "dates",
    where = "location",
    details = "details"
  )
```

# Continuing Education

```{r}
#| label: cont_edu
#| output: asis

cont_edu <- tibble::tribble(
  ~what, ~when, ~where,
  "Spring School in Causal Inference with Observational Data", "04/2022", "Causal Insights, Leeds (UK)",
  "Computational Bayesian methods using brms in R", "02/2022", "Physalia Courses, online",
  "ELIXIR Omics Integration and Systems Biology", "09/2021", "National Bioinformatics Infrastructure Sweden, online",
  "Fundamentals of Epidemiology (EPM101)", "09/2021", "LSHTM, online",
  "Advanced Statistics: Statistical Modelling", "08/2021", "Swiss Institute of Bioinformatics, online",
  "Alpine Exposome Summer School", "06/2021", "Inserm and ATHLETE, online",
  "Metabolomics Data Processing and Data Analysis", "02/2021", "University of Birmingham, online",
  "Mendelian Randomisation", "05/2020", "Imperial College London, online",
  "Image Analysis and Modeling of Complex Biological Dynamics", "09/2017", "University of Wurzburg, Wurzburg (DE)",
  "Effective High Performance Computing Summer School", "07/2017", "CSCS and University of Lugano, Lugano (CH)",
  "MARVEL School on Variationally Enhanced Sampling", "02/2017", "University of Lugano, Lugano (CH)",
  "Advanced Course in Alternatives to Animal Experimentation", "11/2015", "University of Genova, Genoa (IT)"
) |>
  dplyr::mutate(
    when = lubridate::my(when)
  ) |>
  dplyr::arrange(dplyr::desc(when)) |>
  dplyr::mutate(
    when = format(as.Date(when), "%b %Y")
  ) |>
  cvshortevents(
    what = "what",
    when = "when",
    where = "where"
  )
```

# Service

```{r}
#| label: service
#| output: asis

service_raw <- rorcid::orcid_services(orcid = my_orcid)
service <- service_raw$`0000-0003-3031-322X`$`affiliation-group` |>
  dplyr::bind_rows() |>
  tibble::as_tibble() |>
  tidyr::unnest(cols = "summaries") |>
  janitor::clean_names() |>
  dplyr::mutate(
    service_summary_end_date_year_value = tidyr::replace_na(
      service_summary_end_date_year_value, "Present"
    ),
    dates = paste0(
      service_summary_start_date_year_value,
      " - ",
      service_summary_end_date_year_value
    )
  ) |>
  cvshortevents(
    what = "service_summary_role_title",
    when = "dates",
    where = "service_summary_organization_name"
  )
```

# Skills

```{r}
#| output: asis

skills <- tibble::tribble(
  ~what, ~details,
  "Languages", "Italian (native), English (C1, IELTS 7.0), Spanish (basic)",
  "Programming Languages", "R, Python, MATLAB, C",
  "Markup Languages", "LaTeX, RMarkdown",
  "Software Development", "git, SLURM, High Performance Scientific Computing"
) |>
  flextable::flextable() |>
  flextable::delete_part(
    part = "header"
  ) |>
  flextable::bold(
    j = 1,
    bold = TRUE,
    part = "all"
  ) |>
  flextable::font(
    fontname = "Computer Modern"
  ) |>
  flextable::fontsize(
    size = 10
  ) |>
  flextable::border_remove()

skills |>
  flextable::width(
    width = 16.5 * 0.3937 * (dim(skills)$widths / sum(dim(skills)$widths))
  )
```
